\setstretch{2}
\raggedright

%Essay Heading
	Abraham Jhared Flores Azcona \\ Olivia A. Graeve \\ ENLACE 2023 \\ \today

%Title
	\centerline{Application Essay}

%Development
\setlength{\parindent}{.5in}

% * WHAT TO ANSWER ON THE ESSAY: 
% * 	1. Why you want to participate in ENLACE 2023?
% *		2. What is your specific area of interest? (check link)

% * MORE INFO: http://jacobsschool.ucsd.edu/faculty/faculty_bios/

% TODO: Review second draft for redaction and spelling mistakes
% TODO: comment any possible corrections and/or changes with the "Better Comments" format
Many software developers coin the term ``Perpetual Beta'' to a
software product that's improved upon but never published as
an official release. In the philosophy of Stoicism, there is an 
endless cycle of improvement and the embracing of discomfort because
it articulates that hardship makes us stronger.

These two views of different fields of knowledge have been the main
drivers of my work ethic, given the fact that they embrace whatever
the game of life decides against us or in favor of us.
As long as I remember, my drive for learning as a whole began with
reading a collection of children's themed encyclopedias with the
characters of Peanuts, and from there, a search for further 
knowledge by pursuing a college degree.

Although, when attending the lectures for the degree,
something felt underwhelming. Until the arrival of the
historic COVID-19 pandemic, I did not have the proper chance to value
my stance in life in that particular moment of history, nevertheless
as a strike of luck, the drive to be better and not be bitter became
more rooted as the turbulent times moved forward, which molded me into
an athletic person ever since I began to train at the gym; a much more 
critical individual that strengthened his childhood curiosity by reading 
academic papers and, overall, becoming a better individual who felt 
proud of himself with a hunger for more.

Now in the seventh semester of my degree, we had a subject named
``Research Workshop I'' which explained the shortcomings of
redacting the theory of a proper academic paper
that solidified this new passion for research that can only
be described as sobering. Although we are university students
in Mexico, the consensus around these topics is to give the bare
minimum at the research, but to me, it made me consider the realms of
research as an entire professional career path when it felt that I 
was experiencing an analysis paralysis of my future outside of undergrad, 
which was influenced by the fact that the posters promoting the ENLACE 2023 
summer program were around campus at the same time.

This experience will be compelling, so applying to the program
will be an enticing experience to provide my grain of sand to
the search for knowledge, and it'll be a must for amplifying
my professional abilities as a prospect of Computer Systems
Engineering, given the world-renowned rigor that is one of the landmarks
of American Academia. Personally, the research developing inside the
Jacobs School of Engineering is a proper consideration for this matter,
and to be more specific, the realms of the Center for Engineered
Natural Intelligence, given that it has a default multidisciplinary 
emphasis on seemingly unrelated fields such as computing, biology, cognitive
sciences and those akin to it.

Every bit of information that could develop will be
advantageous for ourselves and the rest of the world. 
I am convinced that my admission will be a great addition to the
research efforts of the ENLACE 2023 program.